% Curriculum de Ejemplo

\documentclass[11pt, a4paper]{moderncv}

%Estilo del paquete moderncv, otra opcion es classic
% \moderncvtheme[green]{casual}
\moderncvtheme[blue]{casual}

%Codificacion
\usepackage[utf8]{inputenc}

%Ajuste de margenes de pagina
\usepackage[scale=0.8]{geometry}

\AtBeginDocument{\recomputelengths}

%Datos personales
\firstname{Martín}
\familyname{Paulucci Cornejo}
\title{Currículum Vit\ae}
\email{martin.c.paulucci@gmail.com}
% \photo[64pt]{perfil.jpg}

%---------------------
% Contenido
%---------------------

\begin{document}
\maketitle

\section{Profile}
\cvitem{}{
I'm a Software Engineer that has worked in a wide range of projects, for both startups and well established companies. I specialize in full stack web development and have used several web technologies over the years. The last 4 years I've been focusing on pure JavaScript solutions (Node.js and Angular.js) to build RESTful APIs and realtime single page applications. }

\section{Contact Information}

\cvlistitem{\textbf{Birth Date:} February 22, 1988}
\cvlistitem{\textbf{Address:} Consell de Cent 456 4 4, 08013, Barcelona, Spain}
\cvlistitem{\textbf{Nationality:} Germany \& Argentina }
\cvlistitem{\textbf{E-mail:} \href{mailto:martin.c.paulucci@gmail.com}{martin.c.paulucci@gmail.com}}
\cvlistitem{\textbf{Skype:} martinpaulucci}
\cvlistitem{\textbf{LinkedIn:} \url{ar.linkedin.com/in/martinpaulucci} }
\cvlistitem{\textbf{GitHub:} \url{github.com/mpaulucci} }
\cvlistitem{\textbf{Technical Blog:} \url{medium.com/@mpaulucci} }

\section{Work Experience}

\cventry{March 2014 - present}{Full Stack Engineer (JavaScript)}{Freelance}{Barcelona}{Spain}{
\begin{itemize}
\item GoDaddy, USA: Worked as part of a team in charge of migrating GoDaddy's Web Site Builder from a .NET/SQL tech stack to Node.js/Cassandra.
\item Hack \& Craft, Berlin, Germany: Developed a mesh network of content connected by topic, distributed by embedded widget with AngularJS.
\item Twocashew, London, UK: Developed LiveScreens, a new service that delivers functionality to broadcasters to encourage and allow viewers using `second screens' (connected tablets, smartphones and portable computers) to respond directly to content within live TV shows. Build using Node.js, Amazon Web Services and AngularJS.
\end{itemize} 
}

\cventry{January 2012 - February 2014}{Project Leader (JavaScript)}{Willdom SA}{Buenos Aires}{Argentina}{
I was in charge of all technical decisions of a startup inside WillDom called Acekia, a web based test management tool. Acekia started as an internal tool and evolved into a startup, providing a modern dynamic interface, with lots of features other similar tools lacked. \\ \\
As a Project Leader, I was in charge of intensively working with the business plan, choosing the tech stack and implementing the main architecture of the app. Afterwards, my responsibilities included building and managing a team of two additional developers, as well as methodology orchestration (SCRUM) and development of core features. \\ \\
One of the requisites of the app was that it had to be built with the latests technologies available. The initial prototype was built in Django and the final product was architected as a single page application \& REST json API using AngularJS, Node.js, CoffeScript, MongoDB and Twitter Bootstrap. It supported login with different OAuth/OpenId providers, issue sync with GitHub.}

\cventry{October 2011 - February 2012}{Web Developer (Python)}{Freelance}{Buenos Aires}{Argentina}{Development, bug fixing, performance improvements and deployment of a construction management application, using Python, Django, PostgreSQL, JQuery, Mercurial, nginx.}

\cventry{August 2010 - August 2011}{Software Developer (Java, PHP)}{Intelligenx Inc}{Buenos Aires}{Argentina}{
\begin{itemize}
\item PaginasAmarillas.com \& GuiaMais.com: I maintained the search engine written in Java used as the backend for most yellow pages sites in LATAM. Tasks included bug fixing and implementation of features related to geolocalization.
\item YaSabe.com: I developed a Java web service for a `local search' site using a proprietary search engine similar to Lucene, that provided an interface for the frontend written in PHP. I also implemented the subscription module of the site with Paypal integration and wrote some migration scripts for MongoDB.
\end{itemize}
}

\cventry{March 2009 - September 2009}{Web Developer (PHP)}{Xinergia}{Buenos Aires}{Argentina}{I developed several web applications using the LAMP stack and maintained the internal web framework written in PHP.
}

\section{Education}
\cventry{2006 - 2013}{Computer Engineer}{Buenos Aires University}{Buenos Aires}{Argentina}{}
\cvlistitem{6 year career, equivalent to a bachelor + master degree }
\cventry{2000 - 2005}{Science and Math} {Goethe Schule}{Buenos Aires}{Argentina}{}
\cvlistitem{Deutsches Abitur (German high school degree).}
\cvlistitem{Sprachdiplom I \& II.}

\section{Teaching}
\cventry{May 2010 - December 2010}{Teaching assistant}{Buenos Aires University}{}{}{I was a teaching assistant at an ``Algorithms and Programming II'' course. My responsibilities included correction of exams, group monitoring, and teaching. Topics covered were data structures(lists, trees, graphs) and object oriented programming with C++.}


\section{Other Works}

\cventry{June 2013 - Present}{Invisible.js}{}{}{\url{github.com/invisiblejs/invisible}}{Isomorphic Web Framework written in JavaScript. It lets the programmer define domain models once and use them indistinguishable on the server (Node.js) or client (web browser). Its build on top of Express framework, and has MongoDB and socket.io integration.}

\cventry{June 2011}{pygo1963}{}{}{\url{code.google.com/p/pygo1963}}{Atari Go client developed with Python. Engine with Alpha Beta pruning, communication protocol with subprocesses and sockets, GUI build with PyGame.}


\section{Languages}
%cvlanguage necesitan 3 llaves, cuestiones de formateo del curriculum
\cvlanguage{Spanish}{Native}{}
\cvlanguage{English}{Advanced}{}
\cvlanguage{German}{Advanced}{}

\section{Technical Skills}

\cvitem{Programming}{JavaScript, Python, CoffeeScript, Java, C/C++, PHP, HTML/CSS, Bash.}

\cvitem{Web Technologies}{AngularJS, Express, Django, browserify, grunt, mocha, mongoose, passportJS, socket.io, JQuery, less}

\cvitem{Ops}{AWS, Heroku, Apache, nginx.}

\cvitem{Databases}{MongoDB, Cassandra, MySQL, PostgreSQL.}

\cvitem{Tools}{Git, Mercurial, OSX, ArchLinux, Ubuntu}

\cvitem{Methodologies}{Extreme programming, SCRUM, TDD }

\section{Additional Interests}

\cvlistitem{Functional languages: Lisp, Haskell, Erlang}
\cvlistitem{Data Science, Machine Learning, Artificial Intelligence}

\end{document}
